---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Reproduce the Results of Gerard (2019)

1. Download and Install PEER: <https://github.com/PMBio/peer/wiki>. I had
   to build the R package from the cloned repository, as installing it from
   the source package didn't work for me.
   
2. Download and install powsimR: <https://github.com/bvieth/powsimR>.

3. Install the appropriate R packages
    ```{r, eval = FALSE}
    install.packages(c("seqgendiff",
                       "tidyverse", 
                       "BiocManager", 
                       "vroom", 
                       "fastICA", 
                       "ssvd",
                       "sparsepca",
                       "elasticnet",
                       "doSNOW", 
                       "ggthemes",
                       "latex2exp"))
    BiocManager::install(c("SummarizedExperiment", 
                           "pcaMethods", 
                           "sva",
                           "edgeR",
                           "DESeq2", 
                           "limma"))
    ```

4. Download data from the GTEx portal: <https://gtexportal.org/home/>. You'll
   need to place the following files in the "data/gtex" folder:
   
    1. GTEx_Analysis_2016-01-15_v7_RNASeQCv1.1.8_gene_reads.gct
    3. GTEx_v7_Annotations_SubjectPhenotypesDS.txt
    5. GTEx_v7_Annotations_SampleAttributesDS.txt
    
    I cannot release these data, but it's free to sign up for access to GTEx.

5. Run `make`. To reproduce all of the results in the paper, 
   just type in the terminal
   
    ```{bash, eval=FALSE}
    make
    ```
    
    To just reproduce the results comparing the `powsimR` datasets from the 
    `seqgendiff` datasets, run in the terminal:
    
    ```{bash, eval=FALSE}
    make powsimr
    ```
    
    To just reproduce the differential expression simulations, run in the terminal:
    
    ```{bash, eval=FALSE}
    make diff_exp
    ```
    
    To just reproduce the factor analysis simulations, run in the terminal:
    
    ```{bash, eval=FALSE}
    make FAsims
    ```
    
    To just reproduce the plot of the flexible class of mixtures of binomials
    and negative binomials, run in the terminal:
    
    ```{bash, eval=FALSE}
    make NBplots
    ```
    
    To just reproduce the simulations evaluating the Monte Carlo correlation
    estimator, run in the terminal:
    
    ```{bash, eval=FALSE}
    make corest
    ```


    

